### 2016-10-12 doc/chap-3-refman.tex
Fixed a typo
Fixed a typo in the manual
show all function list and fid -> func in print command of console

generates an Intermediate Representation (IR)
of the  JavaScript code in a given file.
\item \verb!cfgBuild -cfgBuilder:silent!\\
\hspace*{4.8em}\verb!-cfgBuilder:out={out}!\\
\hspace*{4.8em}\verb!-cfgBuilder:dot={dot}!

@@

\item \verb!analyze -analyzer:silent!\\
\hspace*{4.4em}\verb!-analyzer:out={out}!\\
\hspace*{4.4em}\verb!-analyzer:console!\\
\hspace*{4.4em}\verb!-analyzer:html={html}!

@@

The \verb!help! command displays a list of available commands and
the \verb!help <command>! command displays the usage of the \verb!<command>!.
For example:
{\small
\begin{verbatim}
<function[0] top-level: Entry[-1], ()> @test.js:1:1
Iter[0] > help print
usage: print state(-all) ({keyword})
       print block
       print loc {LocName} ({keyword})
       print fid {functionID}
       print worklist
       print ipsucc
       print trace
       print cfg
\end{verbatim}
}
\noindent
shows the usage of the \verb!print! command.

@@

\medskip\noindent
\fbox{\texttt{print fid \{functionID\}}}\\[.2em]
It displays the name and the span information of
a given function id.  For example:
{\small
\begin{verbatim}
<function[0] top-level: ExitExc[-3], ()> @test.js:21:1
Iter[12] > print fid 0
* function name: top-level
* span info.   : test.js:1:1-21:1
\end{verbatim}
}

>>>>

generates an Intermediate Representation (IR)
of the  JavaScript code in a given file.
\item \verb!cfgBuild -cfgBuilder:silent!\\
\hspace*{4.8em}\verb!-cfgBuilder:out={out}!\\
\hspace*{4.8em}\verb!-cfgBuilder:dot={name}!

@@

\item \verb!analyze -analyzer:silent!\\
\hspace*{4.4em}\verb!-analyzer:out={out}!\\
\hspace*{4.4em}\verb!-analyzer:console!\\
\hspace*{4.4em}\verb!-analyzer:html={name}!

@@

The \verb!help! command displays a list of available commands and
the \verb!help <command>! command displays the usage of the \verb!<command>!.
For example:
{\small
\begin{verbatim}
<function[0] top-level: Entry[-1], ()> @test.js:1:1
Iter[0] > help print
usage: print state(-all) ({keyword})
       print block
       print loc {LocName} ({keyword})
       print func {functionID}
       print worklist
       print ipsucc
       print trace
       print cfg
\end{verbatim}
}
\noindent
shows the usage of the \verb!print! command.

@@

\medskip\noindent
\fbox{\texttt{print func (\{functionID\})}}\\[.2em]
It displays the list of functions.
If a function id is given, it displays the name and the span of it.
For example:
{\small
\begin{verbatim}
<function[0] top-level: ExitExc[-3], ()> @test.js:21:1
Iter[12] > print func 0
* function name: top-level
* span info.   : test.js:1:1-21:1
\end{verbatim}
}
